### 2017-04-27 src/algorithm.tex
foo

In this section we present an FPTAS algorithm to the VPN problem.
We are given an instance of the VPN problem 
\begin{align}
D_v = (V_v, A_v)			\\
D_p = (V_p, A_p)			\\
(s_v, t_v, s_p, t_p)	\\
(p_d, b_d, p_c, b_c)	\\
c
\end{align}
For now assume all values are integral and polynomial bounded in the size of the input.

We start with the following:
For an ancestor $a_v$ of $t'_v$ denote by $C(a_v)$ its children.
Let $a_p$ be an ancestor of $t'_p$ we want to find an embedding of minimum cost
of some virtual $c_vt'_v$-path into the node $t'_p$, 
where $c_v \in C(a_v)$.
Observe that once $c_v$ is chosen the arc $(a_v, c_v)$ determines completely
whether a physical path with a feasible bottleneck exists, namely, a physical
path exists if and only if there is a physical $s'_vt'_v$-path containing only
arcs with bandwidth at least $b_d(a_v, c_v)$.
On the other hand, the set of $c_vt'_v$-paths
determine completely the cost (and processing-wise feasibility) of the embedding.
Among all the $c_vt'_v$-paths we want to select the one that minimize the
embedding cost under the processing capacity constraints.
Figure \todo{} depicts the above observations.

\begin{figure}[ht]
\centering
\input{fig-dp}
\end{figure}

\todo{define bn(i, j) to be the bottleneck between i and j}
We claim that $\min(ai, bj)$ can be found efficiently 
\todo{describe how}

\todo{argue about scaling and rounding}

>>>>

In this section we present an FPTAS algorithm to the VPN problem.
We are given an instance of the VPN problem 
\begin{align}
D_v = (V_v, A_v)			\\
D_p = (V_p, A_p)			\\
(s_v, t_v, s_p, t_p)	\\
(p_d, b_d, p_c, b_c, c)	\\
\end{align}
For now assume all values are integral and polynomial bounded in the size of the input.

For a vertex $v$ let $C(v)$ be the set of its children.
Let $O'(s'_v, t'_v, s'_p, t'_p)$ be the optimal embedding of some virtual
$C(s'v)t'_v$-path into the physical vertex $t'_p$ such that the bottleneck
between $s'_p$ and $t'_p$ is at least $b_d(s'_v, t'_v)$.
Let $c_v \in C(s'_v)$ and observe that once $c_v$ is chosen the arc 
$(s'_v, c_v)$ determines completely whether a physical path with a feasible
bottleneck exists, namely, 
a physical path exists if and only if there is a physical $s'_vt'_v$-path containing only
arcs with bandwidth at least $b_d(s'_v, c_v)$.
On the other hand, the set of $c_vt'_v$-paths
determine completely the cost (and processing-wise feasibility) of the embedding.
Figure \todo{} depicts the above observations.

\begin{figure}[ht]
\centering
\input{fig-dp}
\caption[]{
\begin{enumerate*}
\item Computing $O'(s'_v, t'_v, s'_p, t'_p)$.
\item The set of $c_dt'_v$-paths determines completely the cost of the embedding
\item 
The arc $(s'_v, c_d)$ determines completely the connectivity of $s'_p$ and
$t'_p$, i.e. physical arcs with bandwidth less than $b_d(s'_v, c_d)$ can not be
used.
\end{enumerate*}
}
\end{figure}

Among all the $c_vt'_v$-paths we want to select the one that minimize the
embedding cost under the processing capacity constraints.
This can be done... 
\todo{describe how}
Calculating $O'(s'_v, t'_v, s'_p, t'_p)$ can be done simply by finding the
optimal path among all children of $s'_v$.

Let $O(t'_v, t'_p)$ be the optimal embedding of some virtual $s_vt'_v$-path
into some physical $s_pt'_p$-path then $O(t_v, t_p)$ is the global optimal
embedding.
Also $O(t'_v, s_p)$ can be computed efficiently for every $t'_v$ as described
above, and $O(s_v, t'_v)$ is simply the minimum cost of embedding $s_v$ in any
physical vertex $s'_p$ such that a physical $s'_pt'_v$-path exists.
For an arbitrary vertices $t'_v$, and $t'_p$, $O(t'_v, t'_p)$ can be computed
efficiently using dynamic programming with the following recursion formula:
$$
O(t'_v, t'_p) = 
\min_{\substack{
s'_v \in P(t'_v)
\\
s'_p \in P(t'_p)
}}
O(s'_v, s'_p) + O'(s'_v, t'_v, s'_p, t'_p)
$$ 
\todo{argue about scaling and rounding}
